Water Management

### 2020-01-16 Paper/paper.tex
Introduction

	\subsection{Background}
With world population expected to hit 9.7 billion in 2050 and 11.2 billion in 2100, more and more people have to be fed, which will increase the demand of water for agriculture \cite{UN:2019}. Already today, around one third of the world's population live under physical water scarcity \cite{Vörösmarty:2000, Alcamo:2003, Oki and Kanae:2006}. With climate change proceeding, rainfall as the natural influx of lakes will become more volatile in some regions while prolonged dry periods will make water an even more precious resource in other areas \cite{Guhathakurta:2011}. This situation will get even worse due to the projected increase in the demand of water per capita in many regions of the world, driven by lifestyle factors, especially diet \cite{Vörösmarty:2000}. Despite all those challenges, research suggests that just by using water more efficiently, we will be able to meet the acute water, environment and poverty challenges facing us over the next 50 years \cite {Molden:2013}.
Therefore, the optimal allocation and sustainable use of the available water will be of increasing importance in the future.

In this work we want to examine the variations in use of water from a (hypothetical) water reservoir. One of the most important uses of surface water is the irrigation of fields for food production. However, as farming and food production are private enterprises and lakes are public goods, interests of all different parties have to be considered.

@@

The water reservoir to be considered has two stakeholders: farmers, who want to use the water for irrigation purposes and citizens, who want to use the lake for recreational activities. At the beginning of every year we have to decide how much of the water from the reservoir is used for the irrigation of fields, which benefits the farmers' harvest.\\\\
The farmers utility function follows the form

\begin{equation}
	F(x) = \frac{a_1}{1+b_1} * x^{1+b_1}
%	F(x) = -\frac{1}{x}
\end{equation}

@@

During the summer months, citizens benefit from the remaining water due to recreational use (e.g. swimming). This leads to the recreational users' utility function which can be described as

\begin{equation}
  G(s, x) = \frac{a_2}{1+b_2} * (s-x)^{1+b_2}
%  G(s, x) = -\frac{1}{(s-x)^2}
\end{equation}

with the additional paramter $s$ which indicates the water level at the beginning of the year. For recreational users, the preference parameters shell be $a_2 = 2$ and $b_2 = -3$.\\\\

>>>>

	\subsection{Motivation}
With world population expected to hit 9.7 billion in 2050 and 11.2 billion in 2100, more and more people have to be fed, which will increase the demand of water for agricultural uses \cite{UN:2019}. Already today, around one third of the world's population live under physical water scarcity \cite{Vörösmarty:2000, Alcamo:2003, Oki and Kanae:2006}. With climate change proceeding, rainfall as the natural influx of lakes will become more volatile in some regions while prolonged dry periods will make water an even more precious resource in other areas \cite{Guhathakurta:2011}. This situation will get even worse due to the projected increase in the demand of water per capita in many regions of the world, driven by lifestyle factors, especially diet \cite{Vörösmarty:2000}. Despite all those challenges, research suggests that just by using water more efficiently, we will be able to meet the acute water, environment and poverty challenges facing us over the next 50 years \cite {Molden:2013}.
Therefore, the optimal allocation and sustainable use of the available water will be of increasing importance in the future.

@@

In this work we want to examine the variations in use of water from a (hypothetical) water reservoir. One of the most important uses of surface water is the irrigation of fields for food production. However, as farming and food production are private enterprises and lakes are public goods, interests of all different parties have to be considered. The water reservoir to be considered has two stakeholders: farmers, who want to use the water for irrigation purposes and citizens, who want to use the lake for recreational activities. At the beginning of every year we have to decide how much of the water from the reservoir is used for the irrigation of fields, which benefits the farmers' harvest.\\\\
The farmers utility function follows the form

\begin{equation}
	F(x) = \frac{a_1}{1+b_1} * x^{1+b_1}
\end{equation}

@@

During the summer months, citizens benefit from the remaining water due to recreational use (e.g. swimming). This can be described by the recreational users' utility function which is

\begin{equation}
  G(s, x) = \frac{a_2}{1+b_2} * (s-x)^{1+b_2}
\end{equation}

with the additional paramter $s$ that indicates the water level at the beginning of the year. For recreational users, the preference parameters shell be $a_2 = 2$ and $b_2 = -3$.\\\\
